>

### 2020-09-24 manuscript/manuscript.Rmd
Clarify applicability strategy close #13

We compared our utility-based accessibility to a well-constructed isochrone
that has attracted attention in the literature. That said, virtually all tracts
in New York City are within this specific isochrone. It is possible that this 
isochrone may be more discriminating of park access in other cities, or that a
different definition would yield different results in New York City. This
observation however reinforces our suggestion that a measure explicitly based in
the utility of access is warranted.

@@

In both cases a common, isochrone-based analysis estimated a statistically weak
relationship with greater uncertainty. Isochrone analyses are relatively common in
the literature, perhaps because of the widespread availability of and training
in GIS software. In spite of their widespread use, isochrones are relatively
limited in terms of both their theoretical underpinnings and their flexibility
to accommodate attributes of parks beyond their proximity. And even proximity
may not be adequately handled, as the isochrone threshold may be arbitrarily
asserted by the researcher. The model we apply in this paper extends
a more comprehensive and flexible approach
for measuring the impact of park access on health outcomes. Adopting
utility-based accessibilities of the kind used in this study will allow
researchers to encompass the full range of park amenities in their accessibility
analyses, and to separate the definition of access from the study of its effects.
This will in turn enhance the ability of planners to consider how multiple
attributes of a park --- from its location to its size to its amenities and
beyond --- benefit the health of the community the park serves.

>>>>

We compared our utility-based accessibility to a well-constructed isochrone
that has attracted attention in the literature. That said, virtually all tracts
in New York City are within this specific isochrone. It is possible that this 
isochrone may be more discriminating of park access in other cities, or that a
different definition would yield different results in New York City. This
observation however reinforces our suggestion that a measure explicitly based in
the utility of access is warranted.  We acknowledge that a utility-based
framework for access may be more technically difficult for some practitioners to
independently construct for their analyses than an isochrone or even a
gravity-based measure. That said, it may not be necessary for practicing
planners to construct this measure themselves: web-based tools such as ParkIndex
[@Kaczynski2016] and even WalkScore (https://www.walkscore.com) abstract complex
methodologies into tools that planners can and do readily apply.

@@

In both cases a common, isochrone-based analysis estimated a statistically weak
relationship with greater uncertainty. Isochrone analyses are relatively common in
the literature, perhaps because of the widespread availability of and training
in GIS software. In spite of their widespread use, isochrones are relatively
limited in terms of both their theoretical underpinnings and their flexibility
to accommodate attributes of parks beyond their proximity. And even proximity
may not be adequately handled, as the isochrone threshold may be arbitrarily
asserted by the researcher. The model we apply in this paper extends
a more comprehensive and flexible approach
for measuring the impact of park access on health outcomes.

Adopting utility-based accessibilities of the kind used in this study will allow
researchers to encompass the full range of park amenities in their accessibility
analyses, and to separate the definition of access from the study of its
effects. This will in turn enhance the ability of planners to consider how
multiple attributes of a park --- from its location to its size to its amenities
and beyond --- benefit the health of the community the park serves.
